RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2013-12-17 papers/rjournal/eddelbuettel-francois-stokely.tex
Remove latex temporary file from revision control. Add more citations and text to intro.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@557 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\abstract{Modern data collection and analysis pipelines often involve
 a sophisticated mix of applications written in general purpose and
 specialized programming languages.  Protocol Buffers are a popular
 method of serializing structured data between applications---while remaining
 indendent of programming languages or operating system.  The
 \CRANpkg{RProtoBuf} package provides a complete interface to this
 library.
 %TODO(ms) keep it less than 150 words.
}

@@

Modern data collection and analysis pipelines often involve a
sophisticated mix of applications used for collecting, cleaning,
analyzing, processing, and presenting data.  Each stage of the data
analysis pipeline may involve storing intermediate results in a
file or sending them over the network.  Programming langauges such as
Java, Ruby, Python, and R include built-in serialization support, but
these formats are tied to the specific programming language in use.
CSV files can be read and written by many applications and so are
often used for exporting tabular data.  However, CSV files have a
number of disadvantages, such as a limitation of exporting only
tabular datasets, lack of type-safety, inefficient text representation
and parsing, and abiguities in the format involving special
characters.  JSON is another widely supported format used mostly on
the web that removes many of these disadvantages, but it too suffers
from being too slow to parse and also does not provide strong typing
between integers and floating point.  Large numbers of JSON messages
would also be required to duplicate the field names with each message.

@@

\section{Protocol Bfufers}

@@

>>>>

\abstract{Modern data collection and analysis pipelines often involve
 a sophisticated mix of applications written in general purpose and
 specialized programming languages.  Protocol Buffers are a popular
 method of serializing structured data between applications---while remaining
 independent of programming languages or operating system.  The
 \CRANpkg{RProtoBuf} package provides a complete interface to this
 library.
 %TODO(ms) keep it less than 150 words.
}

@@

Modern data collection and analysis pipelines are increasingly being
built using collections of components to better manage software
complexity through reusability, modularity, and fault
isolation \citep{Wegiel:2010:CTT:1932682.1869479}.  Different
programming languages are often used for the different phases of data
analysis -- collection, cleaning, analysis, post-processing, and
presentation in order to take advantage of the unique combination of 
performance, speed of development, and library support offered by
different environments.  Each stage of the data
analysis pipeline may involve storing intermediate results in a
file or sending them over the network.  Programming langauges such as
Java, Ruby, Python, and R include built-in serialization support, but
these formats are tied to the specific programming language in use.
CSV files can be read and written by many applications and so are
often used for exporting tabular data.  However, CSV files have a
number of disadvantages, such as a limitation of exporting only
tabular datasets, lack of type-safety, inefficient text representation
and parsing, and abiguities in the format involving special
characters.  JSON is another widely supported format used mostly on
the web that removes many of these disadvantages, but it too suffers
from being too slow to parse and also does not provide strong typing
between integers and floating point.  Large numbers of JSON messages
would also be required to duplicate the field names with each message.

@@

\section{Protocol Buffers}

@@

TODO(ms): random citations to work in:

We make use of Object Tables \citep{RObjectTables} for lookup.
Many sources compare data serialization formats and show protocol
buffers very favorably to the alternatives, such
as \citep{Sumaray:2012:CDS:2184751.2184810}
